---
title: "arabidopsis.oxygen.project"
author: "Amanda Salvi"
date: "3/2/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls())
library(dplyr)
library(ggplot2)
```

## Oxygen's Effect on Photosynthesis
Control group has lower photosynthesis rate than 12% oxygen group (p = 0.02). Control and 6% oxygen groups have same photosynthesis rates (p = 0.41)

```{r, echo = FALSE}
photo = read.csv("/Users/amandasalvi9/Documents/Barker Projects/Arabadopsis.oxygen.levels/compiled data/ara.oxygen.photo.master.csv")

photo$treatment = factor(photo$treatment,
                levels = c("control","12%", "6%"))

photo %>% ggplot(aes(x=treatment,y=Photo.out)) +
  geom_boxplot() +
  theme_bw()

model_photo = lm(Photo.out ~ treatment + block + subsample, data=photo)
summary(model_photo)  

```
## Let's look at the stomatal conductance too
Stomatal conductance is different among the three species. From lowest to highest: control, 12%, 6%. So decreasing oxygen levels increased stomatal conductance. Interesting that stomatal conductance was highest in 6%, even though photosynthesis rates weren't different from control.

```{r, echo = FALSE}
photo$treatment = factor(photo$treatment,
                levels = c("control","12%", "6%"))

photo %>% ggplot(aes(x=treatment,y=Cond.out)) +
  geom_boxplot() +
  theme_bw()

model_cond = lm(Cond.out ~ treatment + block + subsample, data=photo)
summary(model_cond)  



```

## Oxygen's Effect on Respiration
Respiration not different among the three groups (p=0.33)

```{r, echo = FALSE}
resp = read.csv("/Users/amandasalvi9/Documents/Barker Projects/Arabadopsis.oxygen.levels/compiled data/ara.oxygen.resp.master.csv")

resp$treatment = factor(resp$treatment,
                levels = c("control","12%", "6%"))

resp %>% ggplot(aes(x=treatment,y=Photo.out)) +
  geom_boxplot() +
  theme_bw()

model_resp = lm(Photo.out ~ treatment + block + subsample, data=resp)
summary(model_resp)  

```

## Let's look at night time transpiration (stomatal conductance at induced night time)
Again, treatment 6% oxygen had highest level of stomatal conductance. However, control and 12% were not statistically different.

```{r, echo = FALSE}
resp %>% ggplot(aes(x=treatment,y=Cond.out)) +
  geom_boxplot() +
  theme_bw()

model_resp.cond = lm(Cond.out ~ treatment + block + subsample, data=resp)
summary(model_resp.cond)  

```

##Conclusions
* Different atmospheric oxygen levels change stomatal conductance in Arabidopsis, such that lower oxygen levels tend to increase stomatal conductance. Trying to open stomata to get more oxygen in ?  
* Different oxygen levels don't affect respiration.  
* Different oxygen levels seem to change photosynthesis, at least in 12% group. So maybe there is a "sweet spot" of oxygen levels. Decreasing oxygen levels would decrease rates of photorespiration, which would increase net assimilation rates (which is actually what was measured by the instrument); but decreasing oxygen levels more than that (6%) may result in decreases of true photosynthetic rates, making negligible the decrease in photorespiration, and thus making the 6% treatment the same as the control ?  